### 2013-11-20 regressionModelling.Rmd
Just another test commit whether rawgithub can handle with .css
toc should work now

- [back to index](index.html)

`generated at:`
```{r, echo=FALSE}
Sys.time()
```
---

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit("regressionModelling.Rmd")
system("pandoc -s regressionModelling.md -o regressionModelling.html --toc --number-section")

>>>>

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit2html('regressionModelling.Rmd', options = c('toc', markdown::markdownHTMLOptions(TRUE)))
